CASE DETECTION OF TUBERCULOSIS PATIENTS USING MACHINE-LEARNING

### 2024-04-23 products/manuscript/Manuscript.qmd
improvement 2

```{r }
#| label: tbl-characteristics
#| tbl-cap: " Participants' Characteristics"
#| echo: FALSE
ch<- readRDS(here("results", "tables", "characteristics.rds"))

@@

```{r }
#| label: tbl-model_perfomance_train
#| tbl-cap: "Model_perfomance."
#| echo: FALSE
mpf <- readRDS(here("results", "tables", "model_perfomance_train.rds"))

@@

```{r }
#| label: tbl-Random Forest
#| tbl-cap: " Model Predictions (Random Forest)"
#| echo: FALSE
rf <- readRDS(here("results", "tables", "rfconf_table.rds"))

rf %>%
  kable()
```

@@

```{r }
#| label: fig-Random Forest_Roccurve
#| fig-cap: "Random Forest_Roccurve"
#| echo: FALSE
knitr::include_graphics(here("results","figures", "rf_ROCCURVE.png"))
```

```{r }
#| label: tbl-Support Vector Machine
#| tbl-cap: "  Model Predictions (SVM)"
#| echo: FALSE
svm<- readRDS(here("results", "tables", "svmconf_table.rds"))
svm %>%
  kable()
```

@@

```{r }
#| label: fig-supporter Vector Machine_Roccurve
#| fig-cap: "svm_ROCCURVE"
#| echo: FALSE
knitr::include_graphics(here("results","figures", "svm_ROCCURVE.png"))
```

```{r }
#| label: tbl-LASSO
#| tbl-cap: "  Model Predictions (LASSO)"
#| echo: FALSE
ls<- readRDS(here("results", "tables", "lassoconf_table.rds"))
ls %>%
  kable()
```

@@

```{r }
#| label: fig-Lasso_ROCCURVE
#| fig-cap: "Lasso_ROCCURVE"
#| echo: FALSE 
knitr::include_graphics(here("results","figures", "Lasso_ROCCURVE.png"))
```

```{r}
#| label: model_perfomance_test
#| tbl-cap: "model_perfomance_test"
#| echo: FALSE
tmpf <- readRDS(here("results", "tables", "model_perfomance_test.rds"))

>>>>

```{r echo=FALSE, message = FALSE }

ch<- readRDS(here("results", "tables", "characteristics.rds"))

@@

```{r echo=FALSE, message = FALSE}

mpf <- readRDS(here("results", "tables", "model_perfomance_train.rds"))

@@

```{r echo=FALSE, message = FALSE }
rf <- readRDS(here("results", "tables", "rfconf_table.rds"))
rf %>%
  kable()
```

@@

```{r echo=FALSE, message = FALSE }
knitr::include_graphics(here("results","figures", "rf_ROCCURVE.png"))
```

```{r echo=FALSE, message = FALSE}

svm<- readRDS(here("results", "tables", "svmconf_table.rds"))
svm %>%
  kable()
```

@@

```{r echo=FALSE, message = FALSE}

knitr::include_graphics(here("results","figures", "svm_ROCCURVE.png"))
```

```{r echo=FALSE, message = FALSE}

ls<- readRDS(here("results", "tables", "lassoconf_table.rds"))
ls %>%
  kable()
```

@@

```{r echo=FALSE, message = FALSE}

knitr::include_graphics(here("results","figures", "Lasso_ROCCURVE.png"))
```

```{r echo=FALSE, message = FALSE}

tmpf <- readRDS(here("results", "tables", "model_perfomance_test.rds"))
